### 2020-08-20 thesis/thesis.tex
[thesis] Cite Power's comodels and Uustalu's runners

    We could end by stating this definition, and everything else would follow
    directly from duality. However, expanding definitions is going to give us
    better intuition, as well as give more solid ground for implementation.
    For this part, we are going to assume we operate in \textbf{Set} category.

@@

    Work that is the closest related to topic of the thesis, is work done by
    Danel Ahman and Andrej Bauer~\cite{runners-in-action}, as well as their
    implementation of a $\lambda_{coop}$ language~\cite{coop}, which is a
    calculus that ensures linear usage of resources as well as execution of
    code handling finalisation.

@@

    What was achieved, what was described, what needs to be done or researched.

>>>>

    We could end by stating this definition of comodels~\cite{comodels}, and
    everything else would follow directly from duality. However, expanding
    definitions is going to give us better intuition, as well as give more solid
    ground for implementation. For this part, we are going to assume we operate
    in \textbf{Set} category.

@@

    Work that is the closest related to topic of the thesis, is work done by
    Danel Ahman and Andrej Bauer~\cite{runners-in-action}, as well as their
    implementation of a $\lambda_{coop}$ language~\cite{coop}, which is a
    calculus with runners of coalgebraic effects~\cite{runners-uustalu}
    that ensures linear usage of resources as well as execution of
    code handling finalisation.

@@

    TODO What was achieved, what was described, what needs to be done or researched.
